\begin{frame}[allowframebreaks]
    \frametitle{13.3.1 质量与价格谈判}
    \begin{itemize}
    \item Martin: I agree that yours are of better quality. But there’s competition from synthetic products, too. You can’t very well ignore that. \\
    \small{马丁：我同意你们质量更好。但合成产品也有竞争，这点不容忽视。}
    
    \item Xu: There’s practically no substitute for bristles for certain uses. That’s why demand for natural bristles keeps rising in spite of cheaper synthetic ones. To be frank with you, if it were not for the friendly relationship between us, we would hardly be willing to make you a firm offer at this price. \\
    \small{徐：某些用途上猪鬃是无可替代的。这就是为什么尽管合成品更便宜，天然猪鬃需求仍在增长。坦白说，若非我们的友好关系，我们不会以这个价格报实盘。}
    
    \item Martin: Well, we’ll have a lot of difficulties in persuading our clients to buy at this price. But I’ll have to try, I suppose. \\
    \small{马丁：说服客户接受这个价格会很困难，但我会尽力尝试。}
    \end{itemize}
    \end{frame}
    
    \begin{frame}[allowframebreaks]
    \frametitle{13.3.2 折中方案谈判}
    \begin{itemize}
    \item Jones: Good morning. I am Henry Jones. I came to you yesterday for inquiry about your bed-covers. \\
    \small{琼斯：早上好，我是亨利·琼斯。昨天来咨询过贵方床罩。}
    
    \item Salesman: Oh, Mr. Jones. Nice to see you again. \\
    \small{销售员：琼斯先生，很高兴再次见面。}
    
    \item Jones: Yesterday afternoon, I called my head office in Spain, they are very interested in your bed-covers. \\
    \small{琼斯：昨天下午我联系了西班牙总部，他们对贵方床罩很感兴趣。}
    
    \item Salesman: Good. \\
    \small{销售员：太好了。}
    
    \item Jones: But, there’s one problem. \\
    \small{琼斯：但有个问题。}
    
    \item Salesman: What’ that? \\
    \small{销售员：什么问题？}
    
    \item Jones: Price. The price in your price sheet is much too high. We can in no way sell your bed-covers in our market at your prices. \\
    \small{琼斯：价格。贵方报价单上的价格过高，按此价格我们无法在本地市场销售。}
    
    \item As a matter of fact, bed-cover retail prices here show a downward trend. To make the business possible, I would suggest that you allow us a special discount of, say 6\%, so as to enable us to continue our business with you. \\
    \small{事实上本地床罩零售价呈下降趋势。为促成交易，建议给予6\%特别折扣以便继续合作。}
    
    \item Salesman: Oh sorry. We’ll never be able to bring down our price to your level. You know, our price is closely calculated and the margin of profit is very small. \\
    \small{销售员：抱歉，我们无法降到您要求的水平。我们的价格经过精密计算，利润空间很小。}
    
    \item Jones: I think it unwise for either of us to insist on his own price. How about meeting each other halfway? I only ask you to make a concession of 3\% on your quotation. That’s reasonable, isn’t it? \\
    \small{琼斯：僵持各自价格对双方都不利。各让3\%如何？这个要求很合理吧？}
    
    \item Salesman: To tell you plainly, the price we quoted you yesterday is really the lowest and we cannot stand any cuts. \\
    \small{销售员：实话说，昨日报价已是最低价，无法再降。}
    
    \item Jones: To reduce your cost, I’m prepared to place you a large order of 2,500 dozens. This is certainly a big contract, and in view of our future relations I feel sure you’ll try your best to help me settle the price problem, otherwise my home office will complain about me. That wouldn’t be very good! \\
    \small{琼斯：为降低成本，我准备订购2500打。这是大单，考虑到未来合作，相信贵方会尽力解决价格问题。否则总部将问责于我，这对双方都不好。}
    
    \item Salesman: You certainly have a way of talking me into it. But the best we can do... \\
    \small{销售员：您真会说服人。但我们最多只能...}
    \end{itemize}
    \end{frame}
    